{\bf {\Large Title....}}

### 2016-07-06 ident_manu.Rnw
all heuristics to fig heurist

A set of heuristics was developed to balance the tradeoff in model complexity and identifiability given the challenges described above.  These rulesets were developed with the assumption that parameters will be selected given preference for those with high sensitivity and identifability based on $\gamma < 15$ was an acceptable threshold for subsets (e.g., 93\% accountability between parameters).  Selection heurestics also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences given questions of interest.  In all selection scenarios, parameters were selected by decreasing sensitivity starting with the most sensitive until identifiability did not exceed $\gamma = 15$ where selections were \begin{inparaenum}[1\upshape)]
\item independent of parameter category,
\item blocked within parameter category,
\item or considering all categories equally
\end{inparaenum}.  The selection rules produced seven subsets of parameters that could further be used to optimize model calibration for \ac{do}.

@@

Plotting the raw values from the sensitivity analysis provides a visual assessment of changes (\cref{fig:sensplot}).

\cref{fig:identbox} shows identifiability ranges, describe by caegory, also emphasize that selection indepedent of category may be more appropriate (better identifiability).  Jumps in median suggest inclusion of a specific parameter has disproportionate affect on identifiability.

@@

<<catident, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters by category (optics, organic matter, phytoplankton, temperature, zooplankton).  Parameters are selected in each category by decreasing sensitivity (\\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}). Grey lines indicate thresholds for maximum acceptable identifiability. Selection stops after $\\gamma > 15$ or if the maximum number of parameters in a category is selected.', fig.height = 8.5, fig.width = 4.5, echo = F, cache = TRUE, out.width = '0.6\\textwidth'>>=

@@

# ggplot theme
pthm <- theme_minimal() + 
  theme(
    axis.text.x = element_text(size = 6), 
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    panel.grid.minor = element_blank(), 
    panel.grid.major = element_blank()
    )

# data prep, select all with coll < 15 plus one, as list
toplo <- filter(tocal$cat) %>% 
  split(., .$Category) %>% 
  lapply(function(x){

@@

  }) %>% 
  do.call('rbind', .)

ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_point(size = 3, shape = 21, fill = 'grey') +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  facet_wrap(~Category, ncol = 1, scales = 'free') + 
  scale_x_continuous(breaks = c(1:25)) + 
  scale_y_continuous('Identifiability') +
  pthm

@@

>>>>

A set of heuristics was developed to balance the tradeoff in model complexity and identifiability given the challenges described above.  These rulesets were developed with the assumption that parameters will be selected given preference for those with high sensitivity and identifability based on $\gamma < 15$ was an acceptable threshold for subsets (e.g., 93\% accountability between parameters).  Selection heurestics also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences given questions of interest.  In all selection scenarios, parameters were selected by decreasing sensitivity starting with the most sensitive until identifiability did not exceed $\gamma = 15$ where selections were \begin{inparaenum}[1\upshape)]
\item blocked within parameter category,
\item independent of parameter category,
\item or considering all categories equally
\end{inparaenum}.  The selection rules produced seven subsets of parameters that could further be used to optimize model calibration for \ac{do}.

@@

Plotting the raw values from the sensitivity analysis provides a visual assessment of changes (\cref{fig:sensplo}).

\cref{fig:identbox} shows identifiability ranges, describe by category, also emphasize that selection independent of category may be more appropriate (better identifiability).  Jumps in median suggest inclusion of a specific parameter has disproportionate affect on identifiability.

@@

<<heurist, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters with three different heuristics. Parameters are selected by decreasing sensitivity for all examples (\\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}). The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c). Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability. Selection stops after $\\gamma > 15$ or if the maximum number of possible parameters is selected.', fig.height = 8, fig.width = 8, echo = F, cache = TRUE, out.width = '\\textwidth'>>=

@@

cats <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')

# custom col scale
mycols <- RColorBrewer::brewer.pal(5, 'Set2')
names(mycols) <- cats
cols <- scale_fill_manual(name = 'Category', values = mycols)

# ggplot theme
pthm <- theme_minimal() + 
  theme(
    axis.text.x = element_text(size = 6), 
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    panel.grid.minor = element_blank(), 
    panel.grid.major = element_blank(), 
    axis.title.y = element_blank(), 
    axis.title.x = element_blank()
    )

# top sensitive within categories
toplo <- filter(tocal$cat) %>% 
  split(., .$Category) %>% 
  lapply(function(x){

@@

  }) %>% 
  do.call('rbind', .)
toplo$Category <- factor(toplo$Category, levels = cats, labels = cats)
pcat <- ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_point(size = 3, shape = 21, aes(fill = Category)) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  facet_wrap(~Category, ncol = 1, scales = 'free') + 
  scale_x_continuous(breaks = c(1:25)) + 
  scale_y_continuous('Identifiability') +
  cols +
  pthm +
  theme(legend.position = 'none') +
  ggtitle('(a) Blocked by category')

# top sensitive
toplo <- tocal$top
sel <- which(toplo$coll < 15)
toplo <- toplo[c(sel, rev(sel)[1] + 1), ]
toplo$Category <- factor(toplo$Category, levels = cats, labels = cats)
ptop <- ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_point(size = 4, shape = 21, aes(fill = Category)) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  scale_x_continuous(breaks = 1:nrow(toplo)) + 
  scale_y_continuous('Identifiability') + 
  cols +
  pthm +
  theme(legend.position = 'none') +
  ggtitle('(b) Independent of category')

# top sensitive and category
toplo <- tocal$cattop
sel <- which(toplo$coll < 15)
toplo <- toplo[c(sel, rev(sel)[1] + 1), ]
toplo$Category <- factor(toplo$Category, levels = cats, labels = cats)
pcattop <- ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_point(size = 4, shape = 21, aes(fill = Category)) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  scale_x_continuous(breaks = 1:nrow(toplo)) + 
  scale_y_continuous('Identifiability') +
  cols +
  pthm +
  theme(legend.position = 'top') + 
  ggtitle('(c) All categories equally')

pleg <- g_legend(pcattop)
pcattop <- pcattop +
  theme(legend.position = 'none')

grid.arrange(
  pleg, 
  arrangeGrob(
    pcat,
    arrangeGrob(ptop, pcattop, ncol = 1), 
    widths = c(1, 1),
    ncol = 2
    ), 
  ncol = 1, 
  heights = c(0.05, 1),
  bottom = 'Selected', 
  left = 'Identifiability'
)

@@

<<st>>=
load(file = 'rdata/tocal_all.Rdata')

toplo <- tocal_all$top_all %>% 
  reshape2::melt(., id.var = names(.[[1]]))

ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line(size = 1) + 
  geom_hline(yintercept = 15) +
  geom_label_repel(
    aes(label = Parameter), 
    label.padding = unit(0.1, "lines"),
    box.padding = unit(2, "lines"), 
    force = 2
    ) + 
  geom_point(aes(colour = Category), size = 5) +
  coord_cartesian(ylim = c(0, 25), xlim = c(0, 16)) + 
  theme_classic() + 
  facet_wrap(~L1, scales= 'free_x', ncol = 4) + 
  scale_colour_brewer(palette = 'Set1') + 
  scale_y_continuous('Identifiability') + 
  scale_x_continuous(
    'No. selected by increasing sensitivity',
    breaks=toplo$Selected
    ) + 
  theme(
    legend.position = 'top', 
    strip.text = element_text(size = 12),
    axis.line.x = element_line(size = 0.5),
    axis.line.y = element_line(size = 0.5)
    )
@

### 2016-07-06 ident_manu.tex
all heuristics to fig heurist

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Thu Jun 30 19:09:01 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

{\centering \includegraphics[width=0.6\textwidth]{figs/catident-1}

@@

\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters by category (optics, organic matter, phytoplankton, temperature, zooplankton).  Parameters are selected in each category by decreasing sensitivity (\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}). Grey lines indicate thresholds for maximum acceptable identifiability. Selection stops after $\gamma > 15$ or if the maximum number of parameters in a category is selected.}\label{fig:catident}
\end{figure}

>>>>

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Fri Jul 1 16:59:17 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

{\centering \includegraphics[width=\textwidth]{figs/heurist-1}

@@

\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters with three different heuristics. Parameters are selected by decreasing sensitivity for all examples (\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}). The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c). Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability. Selection stops after $\gamma > 15$ or if the maximum number of possible parameters is selected.}\label{fig:heurist}
\end{figure}
